State of the Practice for Medical Imaging Software

### 2021-12-14 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Simplified the scope section to explicitly state visualization is our scope, and then list what is excluded.  Removed figure.

We need to restrict the scope of MI software that we consider so that the
measurement exercise is feasible within the targeted person month of effort. We
can restrict the scope by selecting a sub-set of the broad range of problems
considered by MI.  Summing the sets of MI tasks from \citet{Bankman2000} and
\citet{Angenent2006}, we have the following problems are solved by MI software:
Segmentation, Registration, Visualization, Enhancement, Quantification,
Simulation, plus three functions for MI archiving and telemedicine systems
(Compression, Storage, and Communication). To this list Wikipedia contributors
\citep{enwiki:1034877594} add Statistical Analysis and Image-based Physiological
Modelling. \citet{Kim2011} adds Feature Extraction, Classification, and
Interpretation. Besides the above major functions, some MI software provides
supportive functions. For example, using Tool Kit libraries VTK
\citep{SchroederEtAl2006} and ITK \citep{McCormick2014}, developers build
software with Visualization and Analysis functions. Finally, Picture Archiving
and Communication System (PACS) helps users to economically store and
conveniently access images \citep{Choplin1992}.

Based on our literature survey, we divided MI software into five sub-groups and
several sub-sub-groups by their major functions, as shown in
Figure~\ref{fig_mi_functions}. We selected the sub-group of Visualization for
the current state of the practice exercise.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{figures/FunctionsOfMiSoftware.pdf}
\caption{Major functions of MI Software} \label{fig_mi_functions}
\end{figure}

>>>>

To make the project feasible, we only cover MI visualization software.  As a
consequence we are excluding many other categories of MI software, including
Segmentation, Registration, Visualization, Enhancement, Quantification,
Simulation, plus MI archiving and telemedicine systems (Compression, Storage,
and Communication) (as summarized by \citet{Bankman2000} and
\citet{Angenent2006}).  We also exclude Statistical Analysis and Image-based
Physiological Modelling \citep{enwiki:1034877594} and Feature Extraction,
Classification, and Interpretation \citep{Kim2011}. Software that provides MI
support functions is also out of scope; therefore, we have not assessed the
toolkit libraries VTK \citep{SchroederEtAl2006} and ITK \citep{McCormick2014}.
Finally, Picture Archiving and Communication System (PACS), which helps users to
economically store and conveniently access images \citep{Choplin1992}, are
considered out of scope.

% Based on our literature survey, we divided MI software into five sub-groups and
% several sub-sub-groups by their major functions, as shown in
% Figure~\ref{fig_mi_functions}.

% \begin{figure}[!ht]
% \centering
% \includegraphics[scale=0.5]{figures/FunctionsOfMiSoftware.pdf}
% \caption{Major functions of MI Software} \label{fig_mi_functions}
% \end{figure}
